Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-05-07 Latex Source/paper.tex
fix spelling add full screenshots
Update paper.tex

\begin{abstract}
A two-part test was conducted to determine if there was a correlation between the effectivness of music versus no music on cognitive response time
and typing efficiency. A participant would take a typing test and qunatified behavioral test (QBTest) with three conditions.
The condiditons would be instrumental music, lyrical music, and lastly no music. While the participant takes the QBTest, the EyeWriter 2.0,
a type of eye tracker, will track the participants eye movements.
Individually the two test were not statistically significant. The typing test's \textit{p} value was 0.1172 whereas the QBTest's \textit{p} value was 0.0818. 
% add results from two tests together
\end{abstract}

@@

\subsection{Eye Tracking and Quantified Behavioral Test}
% if we don't add anything here we can remove this subsection before we submit

% CITATIONS ABOUT EYE TRACKING AND QBTEST HERE

>>>>

\begin{abstract}
A two-part test was conducted to determine if there was a correlation between the effectivness of music versus no music on cognitive response time
and typing efficiency. A participant would take a typing test and quantified behavioral test (QBTest) with three conditions.
The condiditons would be instrumental music, lyrical music, and lastly no music. While the participant takes the QBTest, the EyeWriter 2.0,
a type of eye tracker, will track the participants eye movements.
Individually the two test were not statistically significant. The typing test's \textit{p} value was 0.1172 whereas the QBTest's \textit{p} value was 0.0818. 
% add results from two tests together
\end{abstract}

@@

\subsection{Eye Tracking}
In addition to the aforementioned studies, an innovative approach to eye-tracking technology was presented by \cite{Malaikar2018Arduino}Malaikar et al. (2018) in their work titled "Arduino Based Eye-Writer Using PS3 Eye Camera." This research introduced an eye-tracking device and custom software, known as the Eye-Writer, which aimed to aid individuals with neuromuscular disorders and injuries in drawing or writing using only their eye movements. The Eye-Writer utilized an Arduino platform and a PS3 Eye Camera to track the movement of the user's eyes, enabling creative expression without the need for physical mobility. This novel application of eye-tracking technology showcases the diverse range of potential applications in assistive technology and human-computer interaction.
